### 2016-02-05 Manuscript/BiologyLetters/response.tex

\item{\textcolor{blue}{Along these lines, a 100 character limit may seem rational but this is actually, from a practical perspective, very large. molecular matrices of this size would, of course, be laughed at but many of the most robust phylogenetic studies I'm familiar with come in well under this size. I suspect, but cannot be sure, that this partially explains the poor species level coverage the authors find; higher level studies can readily accumulate large numbers of characters because vastly different morphologies are being compared, often using families or genera as exemplars, leading to an abundance of easily defined characters. Species level studies, on the other, are often focused within families or genera to make them more manageable, but here characters are quickly exhausted. To give some random examples that I'm familiar with, Salles (1992) species-level study of Felidae (all species) was based on 44 characters, Wang and Carranza- Casta\~{n}eda's 2008 study of Mephitidae (\textasciitilde50\% of species but all genera) was based on 38 characters, and Bryant et al's 1993 study of Mustelid genera was of 46 characters. These are all important studies, but do not feature here because of the 100 character limit. At the very least I think this results in a downplaying of previous phylogenetic efforts by morphologists in the results. At worst it misrepresents the state of affairs dramatically. Is 100 really the minimum number you want to go with at all phylogenetic scales?}}

By removing the characters threshold (see above) we now included the taxa coded in Wang and Carranza-Casta\~{n}eda 2008 (matrix reference GS2014-WCC) and other matrices ignored in the former analysis increasing the number of Carnivora from 42 species (14\% of total number of species) to 76 (27\%).
However, the two other matrices mentioned by reviewer 2 (Salles 1992 and Bryant et al. 1993) where not included in the present analysis.
This is due to two main reasons: firstly, these two matrices where not available on any of the matrices repositories (either Graeme Lloyd's, Ross Mounce's or MorphoBank's) and (2) secondly, they didn't matched with out additional Google Scholars search parameters (i.e. matrices published between 2010 and 2015 with accessible data).
Following this reviewer's comment as well as reviewer 4's we added a paragraph in the discussion to clearly state that we are aware of data sampling biases:

``It is worth noting, however, that our analysis did not include all the matrices containing anatomical characters ever published.
In fact, our data collection procedure focused on including studies that provided matrices easily accessible, i.e. we did specifically not include any matrices that were only available in paper format (e.g. printed in books), non-reusable format (e.g. an image of the matrix) %TG: yes... There were quiet a few of them!
or/and matrices available only upon request (e.g. by emailing the authors).
Such matrices are likely to not be included in Total Evidence analysis due to the difficulty of obtaining them.
'' p.@ lines@@.

@@

% NC: Hmmm. I'm concerned about this, and I think your "quick and dirty" solution is pretty dishonest. I think you're going to need to look at your data collection procedure again. 
% First we need to understand *why* is the paper Graham mentions missing? Because you focus on data from 2010 onwards? Because it's not in Graeme or Ross' databases? Need to understand how it got missed out. Does it appear if you get rid of the 10/20 search results only and search lots of results? Is there a problem with search terms? The answer to this will help us decide how to proceed from here.
% NC: Although you don't want to waste a huge amount of time on this, you also don't want a reputation for being sloppy, nor a reputation for glossing over your errors. Also it's important for personal research integrity. If that means you spend two weeks recollecting the data then that will have to be accepted. Note that two weeks is really a very short amount of time in the usual 2 years it takes to write a paper (Martin will be expecting you to have brought some work over from your PhD), but you will need to ask for an extension on the corrections. This won't be a problem. Either way this comment will have to explain how the papers Graham mentions are missed out. If you can do that and it's sensible then explaining the latter point about locating the data is probably fine. And I know you're busy - welcome to the world post PhD! All things happen at once...

We dealt with this comment by removing the matrix size threshold and adding a paragraph to the discussion explaining that some matrices might not be included in this study (see reviewer's 2 comments 1 and 2).
Concerning the Gaubert et al. 2005's study specifically, this study unfortunately did not contain any easily available matrix.
In fact, the matrix mentioned as Appendix 2 in the paper is not present in the article and neither the TreeBase accession numbers (``S1255'', ``M2193'') nor the provided URL (``www.systematicbiology.org'') links to the matrix.
% TG: I don't know if that's a good justification but basically, it's impossible to get this specific matrix.

@@

\item{\textcolor{blue}{One interesting aside that the authors didn't consider, despite the data being there, is how phylogenetic ``effort'' relates to diversity of the order under study.}}

This is a great suggestion, thanks!
We added this analysis to the ESM 2 (Supplementary results - 1) showing, as suggested, that mammalian morphological phylogeneticists have focused their energies on resolving the higher level relationships among mammalian lineages.
We also added a sentence mentioning these results in the manuscript:

``It is also encouraging to note that the sampling effort is consistent with diversity at each taxonomic level and there is therefore no direct bias in sampling at any taxonomic level (ESM 2, Figure 1).
'' p.@ lines@@

### 2016-02-05 Manuscript/BiologyLetters/Supplementary/ESM_2.tex
Changed anatomical characters semantics
Added sampling effort analysis

\noindent{\Large \bf Assessment of cladistic data availability for living mammals}

@@

\section{Supplementary results - 1}
The following section contains supplementary blalbalbal....

@@

>>>>

\noindent{\Large \bf Assessment of available anatomical characters for phylogenetic analysis among living mammals}

@@

\section{Supplementary results - 1}
The following section contains a supplementary analysis looking at the sampling effort for all the mammalian orders at the three different taxonomic levels (family, genus and species).
We calculated linear regressions %TG: does one calculate regressions? I would go for drawing regressions but that's not semantically correct...
between the logged number of sampled taxonomic levels per order against the logged total number of total taxonomic levels and fixed the intercept to 0.
This way we could calculate the slope of the regressions (\textit{b}) indicating the sampling effort (i.e. if the slope is 1, the sampling effort is maximum along each order for the taxonomic level, if 0 there is no significant sampling) and the fit of the regressions (\textit{R$^2$}).
The code for this analysis is available at this link \url{https://github.com/TGuillerme/Missing_living_mammals/blob/master/Analysis/Sampling_effort.R}.

@@

This analysis shows suggests that the sampling effort reflects diversity for each taxonomic level (i.e. morphological characters were collected for each order according to it's size; Figure \ref{Supp_Figure_sampling}).
However, it is worth noting that this relation is stronger at higher taxonomic level (i.e. family, \textit{R$^2$}=0.99 \textit{b}=0.936) in comparison to the species level (\textit{R$^2$}=0.852 \textit{b}=0.711).
These results might be simply due to the increase of elements between each taxonomic levels (i.e. number of species $>$ genera $>$ families)
Nonetheless it is probable that mammalian morphological phylogeneticists did actually focused on resolving higher level relationships among mammalian orders (see Table 1 in the main text).
